ms2

### 2017-05-25 ms2/ms2.Rmd
ms2

all_ineq = read_tsv('data/state_ineq_all_2011.tsv') %>%
  left_join(regions, by='state')
state_ineq = read_tsv('data/state_ineq_2011.tsv')
hrr_ineq = read_tsv('data/hrr_ineq_2011.tsv')
```

@@

```{r nzgini_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient among benes. w/ >= 1 claim') +
theme_minimal()
```

@@

multivariate_term = 'nzgini'
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  # swo> "mean" is a confusing name
  bind_rows(
    linear_model(x, dep, 'mean') %>% mutate(model='univariate'),
    linear_model(x, dep, c('fnz', multivariate_term)) %>% mutate(model='multivariate'),
    spearman_model(x, dep, 'mean') %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

@@

```{r}
interval_plot = function(df) {
  arrange(df, estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>% 
    ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high)) +
    geom_point() +
    geom_linerange() +
    coord_flip()
}

@@

@@

@@

ecoli_bactrim_dat %>%
  { mutate(., excess_resistance=residuals(lm(mean_percent_nonsusceptible ~ mean, data=.))) } %>%
  ggplot(aes(x=nzgini, y=excess_resistance)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  scale_x_continuous(limits=c(0.25, 0.375)) +
  scale_y_continuous(limits=c(-12, 20), breaks=c(-12, 0, 10, 20)) +
  xlab('Skew towards high consumers (Gini coefficient)') +
  ylab('"Excess" E. coli resistance (see caption)') +
  theme_minimal()
```

>>>>

target_year = 2013
all_ineq = read_tsv(sprintf('data/state_ineq_all_%i.tsv', target_year)) %>%
  left_join(regions, by='state')
state_ineq = read_tsv(sprintf('data/state_ineq_%i.tsv', target_year))
hrr_ineq = read_tsv(sprintf('data/hrr_ineq_%i.tsv', target_year))
```

@@

```{r nzgini_mean, cache=FALSE}
ggplot(all_ineq, aes(x=mean, y=nzgini, color=region, label=state_abbreviation)) +
geom_point() +
geom_text(nudge_x=0.04) +
xlab('claims per beneficiary') +
ylab('Gini coefficient') +
theme_minimal()
```

@@

multivariate_term = 'nzgini'
models = function(x) {
  dep = 'mean_percent_nonsusceptible'
  # swo> "mean" is a confusing name
  bind_rows(
    linear_model(x, dep, 'mean') %>% mutate(model='univariate'),
    linear_model(x, dep, c('fnz', multivariate_term)) %>% mutate(model='multivariate'),
    linear_model(x, dep, multivariate_term) %>% mutate(model='uni_nzg'),
    spearman_model(x, dep, 'mean') %>% mutate(model='spearman')
  ) %>%
    mutate(n_data=nrow(x))
}

@@

```{r}
interval_plot = function(df) {
  arrange(df, estimate) %>%
  mutate(bug_drug=interaction(bug, drug_group),
         bug_drug=factor(bug_drug, levels=bug_drug, ordered=TRUE)) %>% 
    ggplot(aes(x=bug_drug, y=estimate, ymin=ci_low, ymax=ci_high, color=drug_group)) +
    geom_point() +
    geom_linerange() +
    coord_flip()
}

@@

## Univariate Gini

```{r}
filter(results, model=='uni_nzg', term=='nzgini') %>%
  arrange(p.value) %>%
  mutate(adj.p=p.adjust(p.value, method='bonferroni')) %>%
  select(bug, drug_group, estimate, p.value, adj.p, n) %>%
  kable
```

@@

```{r}
results %>%
  filter(model=='multivariate') %>%
  filter(term == multivariate_term) %>%
  mutate(bug_drug=interaction(bug, drug_group)) %>%
  ggplot(aes(x=p.value, y=estimate, color=drug_group)) +
  geom_point() +
  scale_color_brewer(palette='Set1')
```

@@

ecoli_bactrim_dat %>%
  { mutate(., excess_resistance=residuals(lm(mean_percent_nonsusceptible ~ mean, data=.))) } %>%
  ggplot(aes(x=nzgini, y=excess_resistance)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  scale_x_continuous(limits=c(0.25, 0.375)) +
  scale_y_continuous(limits=c(-12, 20), breaks=c(-12, 0, 10, 20)) +
  xlab('Skew towards high consumers (Gini coefficient)') +
  ylab('"Excess" E. coli resistance (see caption)') +
  theme_minimal()

ecoli_bactrim_dat %>%
  ggplot(aes(x=nzgini, y=mean_percent_nonsusceptible, label=state)) +
  geom_smooth(method='lm', col='gray', se=FALSE) +
  geom_point() +
  geom_text() +
  xlab('Gini coefficient)') +
  ylab('E. coli resistance') +
  theme_minimal()
```
